Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2019-02-15 ms.tex
show the aperture for grism ap on OTIS long dark

>>>>

\subsection{Grism Aperture}
\begin{figure*}[!hbtp]
\centering
\includegraphics[width=.4\columnwidth]{ap_labels_darkGrismApA5raw_NRCALONG-DARK-7235074213_1.pdf}
\caption{Time series of a grism photometric broadband aperture during a long dark exposure for detector ALONG=A5. As in \ref{fig:longDarkPhot}, the long dark exposure of 108 frames is used to construct 54 pairs of reads that are subtracted, in analogy with a series of integrations.
The photometric aperture is made to represent a similar one to the F322W2 grism trace.
}\label{fig:longDarkGrism}
\end{figure*}
